6.867 Problem Set 3

### 2015-11-11 HW3/tex/HW3.tex

>>>>

We are now interested in testing out neural network code on a real dataset. In our case, we're using a subset the very popular MNIST data collected by Yann Lecunn. This dataset is comprised of 28 by 28 pixel images of handwritten digits with corresponding labels that represent what numbers these images actually represent. For our features, each 28x28 images into a feature vector of 784 where each of these features represent the darkness of a pixel (0 means that its a white pixel, 1 means its a black pixel, everything in between are shades of grey).

When training
